---
title: "Coronavirus EDA"
author: "Savita Sastry"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r}
#install.packages("tidyverse")
#install.packages("naniar")
#install.packages("skimr)
#install.packages("visdat")
library(visdat)
library(tidyverse)
library(naniar)
library(skimr)
```


##Data
**Database of Coronavirus cases by geographical and bodily locaiton of isolation.**  
Reference: Dong E, Du H, Gardner L. An interactive web-based dashboard to track COVID-19 in real time. Lancet Infect Dis; published online Feb 19. https://doi.org/10.1016/S1473-3099(20)30120-1.  
Data: https://www.kaggle.com/brendaso/2019-coronavirus-dataset-01212020-01262020
```{r}
readr::read_csv("data/2019_nCoV_20200121_20200206.csv")
```

**Database of Coronavirus cases by geographical and bodily locaiton of isolation.**  
Reference: Dong E, Du H, Gardner L. An interactive web-based dashboard to track COVID-19 in real time. Lancet Infect Dis; published online Feb 19. https://doi.org/10.1016/S1473-3099(20)30120-1. 
Data: https://www.ncbi.nlm.nih.gov/labs/virus/vssi/#/virus?SeqType_s=Nucleotide&Region_s=Asia&Region_s=Europe&Region_s=North%20America&VirusLineage_ss=Wuhan%20seafood%20market%20pneumonia%20virus,%20taxid:2697049
